---
title: "Poetry Checkpoints"
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(dplyr)
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
```

# Problem 1: Split the poem into lines and create a data frame {#part1}

Here is some example formatted output from a poem selected from each poet's works to give you an idea of what I am expecting your code to produce (for all of the poems, not just for one single poem). 

## Sprog Poem 1

### Poem

[link](https://www.reddit.com/r/AskReddit/comments/gktfx1/whats_something_youre_glad_your_friend_introduced/)


    "Poem for a Friend"

    I know that I don't always see you enough -  
    With work and with kids and a marriage, it's tough.  
    You wake and you take it by dawn and by day -  
    And noon turns to evening, and time slips away. 

    "We'll have to do something," we said when we met -  
    But you and me, brother, we tend to forget.  
    We're working -  
    we're busy -  
    we both try our best -  
    And life doesn't always leave room for the rest.  

    But then, with a smile, I remember it's you.  
    We say that we'll meet, and eventually do.  
    You're there when I need you, and that doesn't end.  
    So buddy, be seeing you... 

    maybe.

    Your friend.

    ^^^:)


### SampleData

I've selected just a few of the original columns to go along with the new columns created while answering this question.

```{r message = FALSE, echo=FALSE}
library(dplyr)
readr::read_csv("checkpoints_data/sprog_checkpoint1.csv", na = "") %>% knitr::kable()
```


## Schnoodle Poem 1

### Poem
[link](https://www.reddit.com/r/velvethippos/comments/v2jnpz/this_little_lady_is_fostering_with_us_she_was)

```
> 'You gotta spoil her rotten'

i was the pup, forgotten,

lived my life out on a chain

you say you'll SpOiL me RoTtEn ?

those are new words for my brain!

don't think that i did nothing wrong,

but now that i am here

i feel like This where i belong -

these humans Like me near!

am learning 'bout this thing called 'trust'

i never felt before

if This is 'spoil', then Please - you Must!

(it's Good, i'm pretty sure...)

my life has been so sad, n tough,

you give me Hope anew

You make me feel I'm Good enough -

You made my Dreams come True!

â¤ï¸



### Sample Data Frame Structure

```{r message = FALSE, echo=FALSE}
readr::read_csv("checkpoints_data/schnoodle_checkpoint1.csv", na = "") %>% head(10) %>% knitr::kable()
```

                              
# Problem 2: Poem Line Stats {#part2}


Note that if you've done any preliminary data cleaning, to e.g. remove quoted lines or trim white space, your answers may differ, and that is fine. 

## Sprog Poem Summary


```{r}
readr::read_csv("checkpoints_data/sprog_checkpoint2.csv", na = "") %>% knitr::kable()
```


## Schnoodle Poem Summary

```{r}
readr::read_csv("checkpoints_data/schnoodle_checkpoint2.csv", na = "") %>% knitr::kable()
```
